---
title: "Projects"
---
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

### Sample Project: Online Grocery Shopping Report

```{r echo=FALSE}
#Load neccessary library
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)
```

```{r echo=FALSE}
#First plot: Show the order and reordered percentage of different aisles, colored by different departments
instacart %>% 
  group_by(aisle,department) %>% 
  summarise(order_n = n(), reorder_n = sum(reordered)) %>% 
  mutate(text_label = str_c("Aisle: ", aisle, '\nDepartment: ', department), order_percent = order_n/nrow(instacart), reorder_perent = reorder_n/order_n) %>% 
  plot_ly(x = ~ order_percent, y = ~ reorder_perent, 
         type = "scatter", mode = "markers", 
         alpha = 0.8,
         color = ~department,
         text = ~text_label) %>%
  layout(xaxis = list(title = "Order Percentage of Aisles"), yaxis = list(title = "Reordered Percentage of Aisles"))
```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;



### Clinical, biochemical and genetic features of patients with mitochondrial diseases
Columbia University Medical Center \ \ \ \ \	Apr – Aug 2018 

+	Merged datasets with more than 50 features for 1,000 patients with SAS procedures including macro
+	Built logistic regression to classify complex disorders and help diseases diagnoses with e1071 in R
+	Utilized goodness of fit test to indicate that the model fits the data


&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

### Retrospective Natural History of Thymidine Kinase 2 Deficiency   
Columbia University Medical Center \ \ \ \ \	Nov – Feb 2018  

+	Incorporated patients’ information from 31 medical centers, and explored and preprocessed data using data cleaning, transformation, segmentations with SAS proc import, merge, proc freq, proc means, etc
+	Constructed statistical models to investigate disease progress pattern of certain population
+	Used chi square test on baseline characteristics to avoid selection bias in R
+	Performed signed-rank test to determine the best treatments for different age groups of people


&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

### Prediction on Parkinson’s Disease Pathway                                                                          
Mount Sinai Health System \ \ \ \ \	May-Sep 2016  

+	Extracted different groups of patients’ information from relational database with MySQL, and interpolated missing values using KNN
+	Constructed regression models to select key factors leading to the disease using caret package in R
+	Presented results with data visualization in Tableau        
